---
title: "Practice Machine Learning Course Project"
author: "Tham Nguyen"
date: "7/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Executive Summary:

This document is the final report of the Peer Assessment project from the Practical Machine Learning course, which is a part of the Data Science Specialization. We will buiding a model for predict the test data (20 case).

## Getting data
we call all the package need for predict project.

```{r ggplot2 readr dplyr caret randomForest}
library(ggplot2)
library(readr)
library(dplyr)
library(caret)
library(randomForest)
```

Read data all data: train and test data
```{r}
train <- read.csv("./data/pml-training.csv")
test <- read.csv("./data/pml-testing.csv")
```

We spend awhile to look at the data
```{r train test}
dim(train)
dim(test)
```

## cleaning data
We will clean all the dataset with resmove some columns.

```{r}
train <- train[, colSums(is.na(train)) == 0] 
test <- test[, colSums(is.na(test)) == 0]
removecols <- nearZeroVar(train)
train <- train[, -removecols]
```

## Data Partitioning
subset data traning to 2 part : traning set - train.sub and testing set - test.sub

```{r 12345 train intrain}
set.seed(12345) 
intrain <- createDataPartition(train$classe, p=0.75, list=F)
train.sub <- train[intrain, ]
test.sub <- train[-intrain, ]
```

## Data Prediction and Modelling
```{r pred_model}
setting <- trainControl(method="cv", 5)
pred_model <- train(classe ~ ., data=train.sub, method="rf", trControl=setting)
pred_model
```
Personally, I am using the  **Random Forest** method in this project course with 5 folds.
According to the result, we can see the result arrange in 5 classes is really good. Let check the Error following to know how this model perform in test data(test.sub). 
(in the limited of this report i just use 1 method but I think result model still good for this data set)

## Cross Validation Testing and Error Estimate
```{r test.sub$classe pred_test}
pred_test <- predict(pred_model, test.sub)
confusionMatrix(test.sub$classe, pred_test)
```
We using pred_model is a predict model for the test.sub data and compare predict result with accuracy data.
As the result, we can see that the R-square is **100%** and the P-Value is **2.2e-16** it show that this model is evaluating for dataset.

## Application model on test data

```{r classe}
classe <- predict(pred_model, test)
classe
```
we use predict model above on the test data to have result of 20 cases that is required in this course project.